---
title: Writing and Research
execute:
  echo: false
  warning: false
comments: false
toc: true
toc-location: left
bibliography: Lula-MyPublications-Broad.bib
---

<!-- # ESEMPI -->
<!-- + (python!) https://ddimmery.com/research -->

<!-- # [setup] -->
 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

if (!require(pacman)) {install.packages(pacman)} 
library(pacman)

# pacman::p_ver("distilltools" )
# pacman::p_exists("distilltools")  # FALSe
# pacman::p_load_gh("EllaKaye/distilltools") # not on CRAN
# 
# pacman::p_ver(  "bib2df")
# pacman::p_exists("bib2df")  #TRUE
# pacman::p_ver_diff(  "bib2df")
# # p_load_gh("ropensci/bib2df") # otherwise warns `as_data_frame() was deprecated in tibble 2.0.0.`

#remotes::install_github("ropensci/bib2df")
p_load(RefManageR,
		 #  bib2df,
		 bibtex,
		 janitor,
		 lubridate,
		 glue,
		 tidyverse, 
		 htmltools,
		 distilltools,
		 bib2df
	)

```

<!-- # [load] -->

<!-- 1.A LOAD & CLEAN ZOTERO'S Lula-MyPublications-Broad.bib -->

```{r  pubs_zot_link}
# - Load bibliography (exported from Zotero)
bib_path <- here::here ("writings","Lula-MyPublications-Broad.bib")

# - as list  (NEEDED for functions later)
mybib <- RefManageR::ReadBib(bib_path, check = FALSE )  #bibtex::do_read_bib(file = bib_path, encoding = "unknown", srcfile)

# - as dataframe
mybib_df_raw <- bib2df::bib2df(bib_path)  

# - Format dataframe version of bibliography
mybib_df <-
	mybib_df_raw %>%
 clean_names() %>%
	select(key = bibtexkey, date, author, 
			 title, journaltitle, doi, 
			 category,type, url, 
			 url_preprint, # added in Zotero tex.url_preprint: https://...
			 file, abstract ) %>%
	mutate(
		# date = parse_date_time(date, "ymd",
		# 							  #select_formats = .select_formats
		# 							  drop = FALSE),
		yyyy_mm = str_sub(date, start = 1, end = 7), # I have some irregularities in format  
		date_parsed = parse_date_time(yyyy_mm,  "ym", truncated = 2 ),
		year = year(date_parsed), 
		month = month(date_parsed)) %>%
	arrange(desc(year), key) %>% 
	dplyr::relocate(c("yyyy_mm" ,    "year" ,        "month"  ), .after =date)

# Set RefManageR options (needed to avoid the "[1]")
oldopts <- RefManageR::BibOptions(
	style = "text",
	bib.style = "authoryear", 
	no.print.fields = c("doi", "url", "urldate", "eprint", "eprinttype"),
	max.names = 50, # maximum number of names to display before using “et al.”
	dashed = FALSE, 
	sorting = "ydnt"
)

# - Load additional metadata
mybib_meta <- tibble::tribble( 
	~"url_pub", ~"url_pdf",~ "url_rg", ~"url_repo", ~"url_arch", ~"url_osf", ~"url_other", ~"url_blog" ) 
mybib_meta[1:nrow(mybib_df), ] <- as.character(NA)

# bind 
mybib_df2 <- cbind(mybib_df, mybib_meta)
# names(mybib_df2)
# rm(mybib, mybib_df, mybib_df_raw, mybib_meta)
```


<!-- # [url] -->

<!-- 2.A (pubs) Distribute **url** column to right columns (which will have the names of icons later) -->
<!-- OKKIO: NEED TO FIX "EXTRA" IN ZOTERO TO MAKE IT WORK ...  -->
```{r  distri_link_pubs}
# ========== Distribute **url** column to right columns (which will have the names of icons later)
# Column A [for this value of col C] <- (like)    Column B [for THE SAME value of col C]
# P-Rev Articles [Official] --> url_pub
mybib_df2$url_pub[mybib_df2$type == "Peer-reviewed"] <- mybib_df2$url[mybib_df2$type == "Peer-reviewed"]
# P-Rev Articles [preprint] --> url_preprint some ERA GIA SALVATO GIUSTO DA SOLO!!!!
# check 
check <-  mybib_df2 [!is.na (mybib_df2$url) & mybib_df2$type != "Peer-reviewed" , c("key", "type", "url")] 
#check
# THESIS in --> url_arch 
mybib_df2$url_arch[ mybib_df2$type == "Thesis" ] <- mybib_df2$url [ mybib_df2$type == "Thesis" ]
# check 
check <-  mybib_df2 [!is.na (mybib_df2$url) & is.na(mybib_df2$url_arch ) & is.na(mybib_df2$url_pub),
							c("key", "type", "url")] 
#check
#  in RG --> url_rg
mybib_df2$url_rg <- ifelse( str_detect(mybib_df2$url, "researchgate.net") ,  mybib_df2$url, mybib_df2$url_rg)
# check 
check <-  mybib_df2 [ !is.na (mybib_df2$url) & 
							 	is.na(mybib_df2$url_arch ) & is.na(mybib_df2$url_pub) & is.na(mybib_df2$url_rg), 
							 c("key", "type", "url")] 
#check
#  Blogs --> url_blog
mybib_df2$url_blog[mybib_df2$type  %in% c("World Bank Blog", "Personal Blog" , "IDB blog") ] <- mybib_df2$url [mybib_df2$type  %in% c("World Bank Blog", "Personal Blog" , "IDB blog") ]
# check 
check <-  mybib_df2 [ !is.na (mybib_df2$url) & 
							 	is.na(mybib_df2$url_pub)  & 
							 	is.na(mybib_df2$url_arch)  & 
							 	is.na(mybib_df2$url_blog)    & 
							 	is.na(mybib_df2$url_rg), 
							 c("key", "type", "url")] 
#check
# ALL the REST -->  url_other (open access)
rest <- check$key
mybib_df2$url_other[which(mybib_df2$key %in% rest) ] <- mybib_df2$url[which(mybib_df2$key %in% rest) ] 
# (GENERAL PDF ) <- NO perche mi incasina !!!!!!!!!!!!!!!!!!!!
# mybib_df2$url_pdf <- ifelse(str_detect(mybib_df2$url, ".pdf$"),  mybib_df2$url, mybib_df2$url_pdf)
# - add some empty column for later 
# mybib_df2$bibtex <- as.character(NA)
mybib_df2$image <- as.logical(NA)

# ========== Restrict options `category2`
mybib_df2$category2[mybib_df2$type == "Peer-reviewed" ] <- "peer-reviewed" # 1 
mybib_df2$category2[mybib_df2$type == "Working Paper" ] <- "working"       # 2 
mybib_df2$category2[mybib_df2$type == "Policy Brief" ] <- "working"
mybib_df2$category2[mybib_df2$type == "Discussion Paper" ] <- "other"        
mybib_df2$category2[mybib_df2$type == "G20 Background Report" ] <- "other"
mybib_df2$category2[mybib_df2$type == "Conference proceedings" ] <- "other"
mybib_df2$category2[mybib_df2$type == "World Bank Blog" ] <- "media"  # 3 
mybib_df2$category2[mybib_df2$type == "Personal Blog" ] <- "media"
mybib_df2$category2[mybib_df2$type == "IDB blog" ] <- "media"
mybib_df2$category2[mybib_df2$type == "Thesis" ] <- "theses"   # 4 
mybib_df2$category2[mybib_df2$type == "Invited Talk" ] <- "conference" # 5 
mybib_df2$category2[mybib_df2$type == "Presentation" ] <- "conference"
# ========== I am an author? 
mybib_df2$lmm <- ifelse(str_detect(mybib_df2$author,  "Mimmi|G20-Italy"), 
								"yes",
								"no")
# names(mybib_df2)
#  [1] "key" "file-pdf"     "date"         "yyyy_mm"      "year"         "month"        "date_parsed"  "author"       "title"       
# [10] "journaltitle" "doi"          "type"         "category"     "category2"    "url"          "url_pub"      "url_preprint" "url_pdf"     
# [19] "url_repo"     "url_arch"     "url_rg"       "url_osf"      "url_other"    "abstract"     "image"       
mybib_df2 <- mybib_df2 %>% 
	dplyr::select ( key,  file,
				date, yyyy_mm, year, month, date_parsed,  
				author, lmm, title, journaltitle, doi,
				type, category, category2, 
				url, #url_pub, 
				url_preprint, url_pdf, url_repo,   
				url_arch, url_rg, url_osf, 
				url_other, url_blog, 
				abstract,   image)

# names of column like Academicons / FA 
# added in `header.html`
mybib_df_acad <- mybib_df2  


#names(mybib_df_acad)[names(mybib_df2) == "url_pub"] <- "elsevier"
names(mybib_df_acad)[names(mybib_df2) == "url_preprint"] <- "preprint"
names(mybib_df_acad)[names(mybib_df2) == "url_pdf"] <- "pdf" # not used 
names(mybib_df_acad)[names(mybib_df2) == "url_repo"] <- "github" # FA
names(mybib_df_acad)[names(mybib_df2) == "url_rg"] <- "researchgate"
names(mybib_df_acad)[names(mybib_df2) == "url_osf"] <- "osf"
names(mybib_df_acad)[names(mybib_df2) == "url_other"] <- "open-access"
names(mybib_df_acad)[names(mybib_df2) == "url_arch"] <- "archive" # FA
names(mybib_df_acad)[names(mybib_df2) == "url_blog"] <- "rss" # FA
```


```{r }
# delete all in env EXCEPT for c(... )
rm(list=setdiff(ls(), c( "mybib_df2", "mybib", "mybib_df_acad")))
```

<!-- # [function] -->
<!-- 3  Functions for formatting a citation {now in R/functions_publications}-->
```{r}
source(here::here("writings", "functions_publications2.R"))
# 
# print_ref_simple(key_select = "mimmi_youth_2009-1",  bib = mytalk)

```




## PUBLICATIONS

```{r}
mybib_df_acad <- mybib_df_acad %>% 
	mutate (file_pdf_path = NA_character_
			  ) %>% 
	mutate(file_pdf_path = case_when( 
		key == "mimmi_natalita_2023" ~ "PDF/IlTicino_sett2023.pdf",
		key == "mimmi_open_2016" ~ "PDF/Ramani_2016.pdf",
		key == "mimmi_sussidiarieta_2009" ~ "PDF/AVSI_2009.pdf",
		
			.default = file_pdf_path
		))



```
 

### Articles in Peer-reviewed Journals
```{r}
#| include: false
mybib_df_acad %>% 
	 filter(category  == "ARTICLE") %>% 
	select(key, type, category, category2)

```
  
`r print_ref_buttons2("mimmi_italy_2024")` <br>
`r print_ref_buttons2("patel_predicting_2022")` <br>
`r print_ref_buttons2("mimmi_informal_2014")` <br>
`r print_ref_buttons2("mimmi_econometric_2010")`

### Technical Reports and Other Publications
```{r}
#| include: false
mybib_df_acad %>% 
	 filter(category  == "REPORT" & lmm == "yes") %>% 
	select(key, type, category, category2)
```


<!-- `r print_ref_buttons2("mimmi_predicting_2017")`<br>  RIPETE PUBBLICAZIONE -->
`r print_ref_buttons2("rodriguez_applying_2014")`<br>
<!-- `r print_ref_buttons2("mimmi_assessing_2012")`<br> RIPETE PUBBLICAZIONE -->
`r print_ref_buttons2("mimmi_should_2012")`<br>
`r print_ref_buttons2("johannes_snapshot_2010")`<br>
`r print_ref_buttons2("mimmi_youth_2009")`

### Technical Reports and Other Publications\*
```{r}
#| include: false
mybib_df_acad %>% 
	 filter(category  == "REPORT" & lmm == "no") %>% 
	select(key, type, category, category2)
```

[(\* *editorial role only*)]{style="color: #cc8400;"} <br><br> 
`r print_ref_buttons2("oecd_building_2021")`<br> 
`r print_ref_buttons2("world_bank_well_2021")`<br> 
`r print_ref_buttons2("daigger_future_2019")`

### Misc. Divulgative Pieces
```{r}
#| include: false
mybib_df_acad %>% 
	 filter(category  == "ONLINE" & lmm == "yes") %>% 
	select(key, type, category, category2)
```

`r print_ref_buttons2("mimmi_natalita_2023")`<br> 
`r print_ref_buttons2("mimmi_senza_2022")`<br> 
`r print_ref_buttons2("mimmi_infrastructure_2021")`<br> 
`r print_ref_buttons2("mimmi_technological_2019")`<br> 
`r print_ref_buttons2("mimmi_predicting_2017-1")`<br> 
`r print_ref_buttons2("mimmi_open_2016")`<br> 
`r print_ref_buttons2("mimmi_sussidiarieta_2009")`


### Theses
```{r}
#| include: false
mybib_df_acad %>% 
	 filter(category  == "THESIS" & lmm == "yes") %>% 
	select(key, type, category, category2)
```


[*Master of Public Policy*]<br>`r print_ref_buttons2("mimmi_demand-driven_2008")`<br>
[*BSc equivalent of Economics & Business Administration*]<br>`r print_ref_buttons2("mimmi_linternazionalizzazione_2001")`

<br> 

<center>
See also [[{{< ai google-scholar >}} Google Scholar Page](https://scholar.google.com/citations?hl=en&user=OBYla5gAAAAJ)  ]{style="color:#9b2374; font-weight:bold; background-color:#ebd3e3;"} and [[{{< ai researchgate >}} ResearchGate Profile](https://www.researchgate.net/profile/Luisa-Mimmi)  ]{style="color:#9b2374; font-weight:bold; background-color:#ebd3e3;"}
</center>
